Dual terminal sliding mode control

### 2016-05-14 paper3_manuscript.tex
20160512

The singularity of the DSM scheme for the robot manipulator can be eliminated by using the technique introduced in \ref{theorem:3}.

@@

>>>>

The singularity of the DSM scheme for the robot manipulator can be eliminated by using the technique introduced in Theorem \ref{theorem:3}.

@@

One can use the term $x^{a/b}$ instead of $sgn^\alpha(x)$ in the dual sliding mode control mentioned above, where $a$ and $b$ are odd numbers with $0<a/b<1$, as the entire proof maintains available theoretically.
\section{Simulation studies}
In this section, two studies will be presented, namely, a verification on the effectiveness of the proposed DSM and MDSM schemes and an application to a manipulator stabilization evaluating the performance of the control schemes.
\subsection{Effectiveness study}
For verifying the effectiveness of the DSM control scheme, consider the following four-order nonlinear system with the disturbance:
\dot x_1 &= x_2\\
\dot x_2 &= x_1^3+0.1\sin(20t)+u_1\\
\dot x_3 &= x_4\\
\dot x_4 &= 0.3\sin(3t)+0.5e^{-3t}+u_2,
\subsection{Performance of the robot manipulator}
